### 2015-12-24 extended-abstract.tex
delete more outline unnecessary for abstract

In this model, there are two phases of interaction between any given industry seeking protection and the ITC. In both cases, all the actors take most-favored-nation (MFN) tariffs as given. In the first phase, when no TTB is in place, an industry exerts effort to convince the ITC to enact a TTB for its product. The ITC then must decide whether the maintain the MFN tariff or impose the TTB barrier. Importantly, we assume that this decision is not deterministic, with the amount of uncertainty varying by industry.

\begin{itemize}
	\item Given that lobby gets an ITC measure in first round of game and it stay stays in place, there is another round five years later; at this point, $\tau^{AD}$ is given
	\item Lobby decides how much effort to put forth given $\tau^{a}$, $\tau^{AD}$, $\ta$
\end{itemize}

The continued imposition of a TTB is not in general costless. We might assume then, that the International Trade Commission (ITC) only grants renewals when it finds the benefits outweigh the costs.

\vskip.3in
\begin{itemize}
	\item If lobbies have to exert effort to achieve higher-than-MFN tariffs, when will it be worthwhile for them to do so?
	\item It's about how hard the lobby lobbies, how much reaction they get
\end{itemize}

\vskip.3in
\begin{itemize}
	\item Note that this is not trade war: foreign is applying $\tau^{*a}$ in most / all cases
		\begin{itemize}
			\item \textbf{Q}: Are all cases of renewal ones of no punishment, i.e. target country is applying MFN tariff?
		\end{itemize}
	\item When is it worth it for lobby to exert effort to renew AD measure?
	\item Lobby must be able to trigger the AD measure in the first place
		\begin{itemize}
			\item This means disputes/non-adherence to MFN tariffs must happen on the equilibrium path
			\item In my model, it is symmetric political uncertainty about how ITC will rule. Why would there be uncertainty?
				\begin{itemize}
					\item Directly about strength of evidence? (indirectly about retaliation / dispute)
					\item Differential valuation about harm to industry---how central the industry is, how politically powerful
					\item \textbf{Q}: What are all the factors that have weight in ITCs decision-making? Are they influenced by other political factors?
					\item Does Congressional uncertainty transfer over to ITC uncertainty?
				\end{itemize}
		\end{itemize}
	\item Why would there be variation in one lobby's incentives between $t=1$ (original application of AD) and $t=6$ when it comes up for renewal?
		\begin{itemize}
			\item Uncertainty could be an answer, \textit{and} it varies across industry
			\item \textbf{Q}: Is this a plausible story?
		\end{itemize}
\end{itemize}

>>>>

In this model, there are two phases of interaction between any given industry seeking protection and the ITC. In both cases, all the actors take most-favored-nation (MFN) tariffs as given. \\

In the first phase, when no TTB is in place, an industry exerts effort to convince the ITC to enact a TTB for its product. The ITC then must decide whether the maintain the MFN tariff or impose the TTB barrier. Importantly, we assume that the decisions of the ITC are not deterministic, with the amount of uncertainty varying by industry. \\

Given that the industry receives temporary protection in the first phase of interaction, there will be another phase of interaction when the trade barrier expires, here modeled as five years later to match the typical five years sunset provision under the WTO. At this point, the interaction is essentially the same with the industry first exerting effort and then the ITC deciding whether to extend the TTB or to revert to the MFN tariff. The essential strategic difference is that at this point the level of the TTB is taken as exogenously set at the level determined in the first round of interaction. \\

An industry's decision about how much, if any, effort to exert depends on a number of factors. Among them are the gap between the applied tariff it faces and the protection it would receive under a TTB, the cost of seeking the TTB, and, crucially, the probability that its request will be granted. That it, the industry's incentives to seek protection, and the intensity with which it does so, depend on how much uncertainty it faces in the ITC's decision-making process. \\

Thus we turn to the question of how the ITC decides whether to grant a TTB. The imposition of a TTB, or continuation of one already in place, is not in general costless. We might assume then, that the ITC only grants renewals when it finds the benefits outweigh the costs. If the ITC's rulings are uncertainty from the point of view of the lobby, it must be that the lobby cannot perfectly predict how the

\vskip.3in
		\begin{itemize}		
			\item In my model, it is symmetric political uncertainty about how ITC will rule. Why would there be uncertainty?
				\begin{itemize}
					\item Directly about strength of evidence? (indirectly about retaliation / dispute)
					\item Differential valuation about harm to industry---how central the industry is, how politically powerful
					\item \textbf{Q}: What are all the factors that have weight in ITCs decision-making? Are they influenced by other political factors?
					\item Does Congressional uncertainty transfer over to ITC uncertainty?
				\end{itemize}
		\end{itemize}
	\item Why would there be variation in one lobby's incentives between $t=1$ (original application of AD) and $t=6$ when it comes up for renewal?
		\begin{itemize}
			\item Uncertainty could be an answer, \textit{and} it varies across industry
			\item \textbf{Q}: Is this a plausible story?
		\end{itemize}
